---
title: "Customer Success Analysis for Swire Coca-Cola"
author: "Vicky Mao, Katelyn Candee, Li Xiang"
date: "2023-04-04"
output:
  html_document:
    theme: yeti
    highlight: tango
    number_sections: yes
    toc: yes
    toc_depth: 3
    toc_float: true
    fig_width: 15
    fig_height: 10
  pdf_document:
    toc: yes
editor_options:
  chunk_output_type: console
---

# Business Problem 
Swire Coca-Cola is seeking a solution to predicting the longevity and profit of new potential customer from local businesses.

# Analytics objective
The objective of this analytics task is to predict customer longevity (in month) and total gross profit for new customers.Swire Coca-Cola will use the results to gauge new customer profitability and develop new customer contracts.

# Questions
1.What target variables should be used to predict customer success ?

2.What kind of relationships are found between target variables and predictors ?

3.What Census data should be used ？

4.Which predictors should be included ?

5.Which prediction models should be used?

6.What are the common characteristics of well-performing customers based on prediction outcomes?

# Approach

To solve the business problem, we will first start by cleaning, filtering and combing the datasets as well as adding census data. Second of all,  we will explore the combined data, looking for patterns, trends, variable importance and relationships. After deciding our predictors, we will test out a few prediction models and select our best model based on model performances. 
Finally, we plan to look for characteristics of "successful" customers based on preciction outcomes and provide the sponsor a conclusion and suggestions. 

# Details

This project will be completed by student team members Katelyn Candee, Li Xiang and Vicky Mao by April 13, with progress checkpoints overseen by University of Utah faculty advisor Jeremy Morris on or before the following dates:<br> 1.
Exploratory data analysis - February 19 <br> 2.
Model selection, evaluation and deployment - March 19<br> 3.
Practice project presentation - April 9<br>

Project team members may be reach at:<br> 1.
Katelyn Candee - (203) 823-3129 - [u1398566\@utah.com](mailto:u1398566@utah.com){.email} <br> 2.
Li Xiang - (385) 335-4332 - [u1328517\@utah.edu](mailto:u1328517@utah.edu){.email}<br> 3.
Vicky Mao - (801) 970-0482 - [u1132288\@utah.edu](mailto:u1132288@utah.edu){.email}<br>


# Data Pre-processing
* Load customer data
* Load sales data
* Clean, trim and summarize sales data
  * Extract only total of selected varibles  and maximum posting date by customer
* Clean and trim customer data
  * Clean zip codes and add state variable
  * Filter to only show "UT" data
  * Add census data
    * Total population
    * Median household income
    * Median gross rent
    * Median housing costs
* Join customer data with sales data
  * Calculate and classify customer longevity(month) by subtracting on-boarding date from maximum posting data
  * Clean NAs
  

Read & Summarize Data

```{r Load raw data}
# Load packages
library(tidyverse)
library(dplyr)

# Set working directory
setwd("~/Desktop/Capstone/")

# Import data sets
customer <- read.csv("FSOP_Customer_Data_v2.0.csv", stringsAsFactors = FALSE)
sales <- read.csv("FSOP_Sales_Data_v2.0.csv", stringsAsFactors = FALSE)

# View Datasets
summary(customer)
summary(sales)

```


From the sale data, we extract total sales,Discount,Invoice Price... and overall maximum posting date by Customer Number. Maximum posting date will be used later to calculate one of our target variables, "Customer Longevity".
```{r Clean and summarize sales data}
# Convert date variables to dates
sales$MIN_POSTING_DATE <- as.Date(sales$MIN_POSTING_DATE)
sales$MAX_POSTING_DATE <- as.Date(sales$MAX_POSTING_DATE)
#customer$ON_BOARDING_DATE <- as.Date(customer$ON_BOARDING_DATE, format = "%m/%d/%Y")

# Convert remaining character type variables to factors
sales <- sales %>%
  mutate_if(is.character, as.factor)

# Extract total sales and maximum max posting date by customer
sales <- sales %>%
  group_by(CUSTOMER_NUMBER_BLINDED) %>%
  summarize(GROSS_PROFIT_DEAD_NET = sum(GROSS_PROFIT_DEAD_NET),
             DISCOUNT = sum( DISCOUNT),
            INVOICE_PRICE = sum(INVOICE_PRICE),
            DEAD_NET = sum(DEAD_NET),
            PHYSICAL_VOLUME = sum(PHYSICAL_VOLUME),
            COGS = sum(COGS),
            NUM_OF_TRANSACTIONS = sum(NUM_OF_TRANSACTIONS),
            MIN_POSTING_DATE = min(MIN_POSTING_DATE),
            MAX_POSTING_DATE = max(MAX_POSTING_DATE))
```

Add "state" to customer data set. This will be used to request American Community Survey data from the Census Bureau.
```{r Clean customer zip codes and add state}

#library(zipcodeR)

# Clean zip codes
customer$ADDRESS_ZIP_CODE <- substr(customer$ADDRESS_ZIP_CODE, 0, 5)

# Obtain data frame of states by zip code
zipcode_state <- zipcodeR::zip_code_db %>%
  select(zipcode, state) %>%
  rename(ADDRESS_ZIP_CODE = zipcode,
         ADDRESS_STATE = state)

# Merge states with customer data set and filter to only UT customers
customer <- left_join(customer, zipcode_state, by = "ADDRESS_ZIP_CODE") %>%
  filter(ADDRESS_STATE == "UT")

# Check for missing state values after merge
sum(is.na(customer$ADDRESS_STATE))

# Identify city-zip code combinations missing values for imputing
customer[is.na(customer$ADDRESS_STATE), ] %>%
  select(ADDRESS_CITY, ADDRESS_ZIP_CODE, ADDRESS_STATE) %>%
  distinct(ADDRESS_CITY, ADDRESS_ZIP_CODE)

# Recheck for missing state values after merge
sum(is.na(customer$ADDRESS_STATE))

# Convert all character type variables to factor type
customer <- customer %>%
  mutate_if(is.character, as.factor)

```

The focus of this analysis is Swire Coca-Cola's B2B restaurant segment, so we filter our sample to include only customers assigned the "Eating & Drinking" activity cluster and labelled as a "Direct Store Delivery (DSD)" business type.
 
```{r Filter down customer data to Eating & Drinking and DSD}
# Save filtered customer data set
customer <- customer %>%
  filter(CUSTOMER_ACTIVITY_CLUSTER_DESCRIPTION == "Eating & Drinking" &
           BUSINESS_TYPE_EXTENSION_DESCRIPTION == "DSD")
```

Extract the following information by "county" from the American Community Survey administered by the U.S. Census Bureau:
* Total population
* Median household income (in the last 12 months)
* Median gross rent
* Median monthly housing costs
* Selected monthly owner costs
* Average household size
* Aggregate number of vehicles used to commute to work
* Median year structure built
* Number of households without internet access


```{r Extract Census data by county}
library(tidycensus)
# Store key for Census Bureau API 
census_key <- readLines("census_key.txt")
census_api_key(census_key)

# Look up all available variables in ACS5 Census data
census_var_all <- load_variables(2021, "acs5",cache = TRUE)

 # Extract ACS5 census data by county
 census_data <- get_acs(geography = "county",
                       state = levels(customer$ADDRESS_STATE),
                       variables = c("B01003_001", "B19019_001",
                                     "B25064_001", "B25105_001",
                                     "B25094_001", "B25010_001",
                                     "B08015_001", "B25035_001",
                                     "B28011_008"),
                       year = 2021) %>%
  select(NAME, variable, estimate) %>%
  separate(NAME, c("COUNTY", "ADDRESS_STATE"), sep = ", ") %>%
  mutate(COUNTY = str_remove_all(COUNTY, " County"),
         COUNTY = str_to_upper(COUNTY),
         ADDRESS_STATE = state.abb[match(ADDRESS_STATE, state.name)],
         variable = case_when(variable == "B01003_001" ~ "TOTAL_POP",
                              variable == "B19019_001" ~ "MED_INCOME",
                              variable == "B25064_001" ~ "MED_GROSS_RENT",
                              variable == "B25105_001" ~ "MED_HOUSING_COST",
                              variable == "B25094_001" ~ "MONTHLY_OWNER_COSTS",
                              variable == "B25010_001" ~ "AVG_HOUSEHOLD_SIZE",
                              variable == "B08015_001" ~ "AGG_NUM_VEHICLES",
                              variable == "B25035_001" ~ "MED_YEAR_BUILT",
                              variable == "B28011_008" ~ "NO_INTERNET")) %>%
  spread(variable, estimate) %>%
  mutate_if(is.character, as.factor)

```

Join the census data with our customer data.
```{r Join census data}
# Join census data with customer data
customer <- left_join(customer, census_data,  
                      by = c("COUNTY", "ADDRESS_STATE")) 

# Check merging census data did not introduce missing values
cbind(
   lapply(
lapply(customer, is.na), sum))

```


Join the customer data with the summarized sales data .
```{r Join sales and customer data}
# Left-join customer data with summarized sales data
customer_sales <- left_join(customer, sales, by = "CUSTOMER_NUMBER_BLINDED")

# Check & clean join make sure there is no missing values
sum(is.na(customer_sales))
```

Calculate "customer longevity" by subtracting "on-boarding date" from "maximum posting date"
```{r}
library(lubridate)
# Extract on-boarding year from on-boarding date
customer_sales$LONGEVITY <- time_length(
  difftime(customer_sales$MAX_POSTING_DATE, 
           customer_sales$ON_BOARDING_DATE),
  "year")

```


# Exploring Data & Predictors

* Check for correlation
* Create base linear models to check relationships and base R^2
* Develop randomForest to eliminate predictors and prevent overfiting 
* Create new linear models after predictor elimination 


```{r include = FALSE}
library(psycho) 
library(tidyverse)
library(ggplot2)
library(caret)
library(rpart)
library(e1071)
library(caret)
library(randomForest)
library(glmnet)
```

Check correlation between selected variables. LONGEVITY is not highly correlated with any other varibles, however, GROSS_PROFIT_DEAD_NET is highly correlated with DEAD_NET, INVOICE_PRICE, DISCOUNT, etc.
```{r}
# Checking for multicollinearity and plotting correlations between predictors
correl <- cor(customer_sales[c(19,20,21,22,24,26,27,28,29,30,31,32,33,36)])
ggcorrplot::ggcorrplot(correl,hc.order=TRUE, type="lower",lab=TRUE) 
cor(correl)
```


Checking linear relationship between LONGEVITY - GROSS_PROFIT_DEAD_NET, the relationship is positive but not strong.
```{r}
# LONGEVITY - GROSS_PROFIT_DEAD_NET
model_lm_GROSS_PROFIT <- lm(LONGEVITY ~ GROSS_PROFIT_DEAD_NET, data = customer_sales)
summary(model_lm_GROSS_PROFIT)

# Relationship visulization
ggplot(customer_sales,aes(x = GROSS_PROFIT_DEAD_NET, y =LONGEVITY)) + geom_point() +geom_smooth(method = "lm")
```


Linear regression for LONGEVITY, r² is 0.1345, Many NA coefficient varibles
```{r}
#Linear Model for Longevity
lm_LONGEVITY <- lm(customer_sales,formula=LONGEVITY ~  SALES_OFFICE_DESCRIPTION +DELIVERY_PLANT_DESCRIPTION +COUNTY+CUSTOMER_TRADE_CHANNEL_DESCRIPTION+CUSTOMER_SUB_TRADE_CHANNEL_DESCRIPTION+ CUSTOMER_TRADE_CHANNEL_DESCRIPTION2+ AGG_NUM_VEHICLES+AVG_HOUSEHOLD_SIZE+ MED_GROSS_RENT+MED_HOUSING_COST+MED_INCOME+MED_YEAR_BUILT+MONTHLY_OWNER_COSTS+TOTAL_POP+DISCOUNT+NUM_OF_TRANSACTIONS)

summary(lm_LONGEVITY)
```



Linear Regression for GROSS_PROFIT_DEAD_NET,r² is 0.8556, Many NA coefficient varibles
```{r}
#Linear model for GROSS_PROFIT_DEAD_NET
lm_Profit <- lm(customer_sales,formula= GROSS_PROFIT_DEAD_NET ~  SALES_OFFICE_DESCRIPTION+DELIVERY_PLANT_DESCRIPTION+COUNTY +CUSTOMER_TRADE_CHANNEL_DESCRIPTION+CUSTOMER_SUB_TRADE_CHANNEL_DESCRIPTION + CUSTOMER_TRADE_CHANNEL_DESCRIPTION2+DISCOUNT+NUM_OF_TRANSACTIONS+ AGG_NUM_VEHICLES+AVG_HOUSEHOLD_SIZE+ MED_GROSS_RENT+MED_HOUSING_COST+MED_INCOME+MED_YEAR_BUILT+MONTHLY_OWNER_COSTS+TOTAL_POP)

summary(lm_Profit)
```


Split Data into train & test
```{r}

#Filter data for LONGEVITY & GROSS_PROFIT_DEAD_NET
CS_L_filtered <- customer_sales [, -c(1,4,5,6,8,9,17,27,29,30,31,32,34,35)]
CS_P_filtered <- customer_sales [, -c(1,4,5,6,8,9,17,29,30,31,32,34,35,36)]

#Split Data tp train and test for LONGEVITY
split = 0.7
trainIndex_L<-createDataPartition(CS_L_filtered$LONGEVITY, p=split, list = FALSE)
train_L<-CS_L_filtered[trainIndex_L, ]
test_L<- CS_L_filtered[-trainIndex_L,]

#Split Data tp train and test for GROSS_PROFIT_DEAD_NET
trainIndex_P<-createDataPartition(CS_P_filtered$GROSS_PROFIT_DEAD_NET, p=split, list = FALSE)
train_P<-CS_P_filtered[trainIndex_P, ]
test_P<- CS_P_filtered[-trainIndex_P,]

```


Class Tree and check for variable importance for LONGEVITY
```{r}
# Organize Variables to include in Random Forest, same as the variables used in lm regression above
tree_x_L <- factor(c("SALES_OFFICE_DESCRIPTION","DELIVERY_PLANT_DESCRIPTION","COUNTY","CUSTOMER_ACTIVITY_CLUSTER_DESCRIPTION",
"CUSTOMER_TRADE_CHANNEL_DESCRIPTION","CUSTOMER_SUB_TRADE_CHANNEL_DESCRIPTION","CUSTOMER_TRADE_CHANNEL_DESCRIPTION2",
"AGG_NUM_VEHICLES","AVG_HOUSEHOLD_SIZE","MED_GROSS_RENT","MED_HOUSING_COST","MED_INCOME","MED_YEAR_BUILT","MONTHLY_OWNER_COSTS","TOTAL_POP", "DISCOUNT","NUM_OF_TRANSACTIONS" ))
   
# Fitting Random Forest to the train dataset
set.seed(120)  
classifier_RF_L = randomForest(x = train_L[,tree_x_L],
                             y = train_L$LONGEVITY,
                             ntree = 500)
classifier_RF_L

# Plotting model
plot(classifier_RF_L)

# Importance plot
importance(classifier_RF_L)
  
# Variable importance plot
varImpPlot(classifier_RF_L)

```

Class Tree and check for variable importance for GROSS_PROFIT_DEAD_NET
```{r}
# Organize Variables to include in Random Forest, same as the variables used in lm regression above
tree_x_P <- factor(c("SALES_OFFICE_DESCRIPTION","DELIVERY_PLANT_DESCRIPTION","COUNTY","CUSTOMER_TRADE_CHANNEL_DESCRIPTION", "CUSTOMER_SUB_TRADE_CHANNEL_DESCRIPTION","CUSTOMER_TRADE_CHANNEL_DESCRIPTION2","DISCOUNT","AGG_NUM_VEHICLES","AVG_HOUSEHOLD_SIZE","MED_GROSS_RENT", "MED_HOUSING_COST","MED_INCOME","MED_YEAR_BUILT","MONTHLY_OWNER_COSTS","TOTAL_POP"))

# Fitting Random Forest to the train dataset
set.seed(120)  
classifier_RF_P = randomForest(x = train_P[,tree_x_P],
                             y = train_P$GROSS_PROFIT_DEAD_NET,
                             ntree = 500)
classifier_RF_P

#Plot
plot(classifier_RF_P)
# Importance plot
importance(classifier_RF_P)
  
# Variable importance plot
varImpPlot(classifier_RF_P)

```





# Modelling

We fit three different model types to predict customer longevity and gross profit:

* Multi Regression
* Lasso
* Ridge
* Kvsm
* Gbm
* Model results comparison


## Predicting LONGEVITY

Multi Regression for LONGEVITY
```{r}
# Define matrix of predictor variables from train
train_x_L <- data.matrix(train_L[,c("SALES_OFFICE_DESCRIPTION","COUNTY","CUSTOMER_TRADE_CHANNEL_DESCRIPTION",
"DELIVERY_PLANT_DESCRIPTION","CUSTOMER_SUB_TRADE_CHANNEL_DESCRIPTION","DISCOUNT","AGG_NUM_VEHICLES","AVG_HOUSEHOLD_SIZE",
"MED_HOUSING_COST","MONTHLY_OWNER_COSTS","TOTAL_POP")])

# Define response variable
train_y_L <- train_L$LONGEVITY

# Define matrix of predictor variables from test
test_x_L <- data.matrix(test_L[,c("SALES_OFFICE_DESCRIPTION","COUNTY","CUSTOMER_TRADE_CHANNEL_DESCRIPTION", "DELIVERY_PLANT_DESCRIPTION","CUSTOMER_SUB_TRADE_CHANNEL_DESCRIPTION","DISCOUNT","AGG_NUM_VEHICLES","AVG_HOUSEHOLD_SIZE", "MED_HOUSING_COST","MONTHLY_OWNER_COSTS","TOTAL_POP")])
test_y_L <- test_L$LONGEVITY

# Multi regression
model_lm_L <- lm(LONGEVITY ~SALES_OFFICE_DESCRIPTION+ COUNTY+DELIVERY_PLANT_DESCRIPTION +CUSTOMER_TRADE_CHANNEL_DESCRIPTION+CUSTOMER_SUB_TRADE_CHANNEL_DESCRIPTION+DISCOUNT +AGG_NUM_VEHICLES+AVG_HOUSEHOLD_SIZE+MED_HOUSING_COST+MONTHLY_OWNER_COSTS+TOTAL_POP,
               data = train_L)
summary(model_lm_L)
summary(train_L)
#Predict
lm_L_predictions <- model_lm_L %>% predict(test_L)

# Overall fit of the prediction model,RMSE & R^2 & MAE
lm_fit_L <- postResample(lm_L_predictions, test_L$LONGEVITY)

# Overall fit of the prediction model,MSE
mse_lm_L <- mean((test_y_L - lm_L_predictions)^2)
print(paste("Test set mean squared error:", mse_lm_L))
```

Ksvm Model for LONGEVIT
```{r}

library(kernlab)
# Train ksvm model with default settings
set.seed(123)
ksvm_L <- ksvm(train_L$LONGEVITY ~ SALES_OFFICE_DESCRIPTION+ COUNTY+DELIVERY_PLANT_DESCRIPTION +CUSTOMER_TRADE_CHANNEL_DESCRIPTION+CUSTOMER_SUB_TRADE_CHANNEL_DESCRIPTION+DISCOUNT +AGG_NUM_VEHICLES+AVG_HOUSEHOLD_SIZE+MED_HOUSING_COST+MONTHLY_OWNER_COSTS+TOTAL_POP,
                data = train_L)

# Overall fit of the prediction model,RMSE & R^2 & MAE
ksvm_predictions_test_L <- predict(ksvm_L,test_L)
ksvm_fit_L <- postResample(ksvm_predictions_test_L, test_L$LONGEVITY)

# Overall fit of the prediction model,MSE
mse_ksvm_L <- mean((test_y_L - ksvm_predictions_test_L)^2)
print(paste("Test set mean squared error:", mse_ksvm_L))

```


Gbm Model for LONGEVITY
```{r}
library(gbm)
# Fit a gradient boosting regression model with 100 trees and 0.01 shrinkage
gbm_L = gbm(train_L$LONGEVITY ~ SALES_OFFICE_DESCRIPTION+ COUNTY+DELIVERY_PLANT_DESCRIPTION +CUSTOMER_TRADE_CHANNEL_DESCRIPTION+CUSTOMER_SUB_TRADE_CHANNEL_DESCRIPTION+DISCOUNT +AGG_NUM_VEHICLES+AVG_HOUSEHOLD_SIZE+MED_HOUSING_COST+MONTHLY_OWNER_COSTS+TOTAL_POP,
                data = train_L,
                distribution = "gaussian",
                cv.folds = 10,
                shrinkage = .01,
                n.minobsinnode = 10,
                n.trees = 500)
 

gbm_predictions_test_L <- predict.gbm(gbm_L, test_L)

# Evaluate the performance of the model on the test set
gbm_fit_L <- postResample(gbm_predictions_test_L, test_L$LONGEVITY)
mse_gbm_L <- mean((test_L$LONGEVITY - gbm_predictions_test_L)^2)
print(paste("Random Forest Regression MSE:", mse_gbm_L))
```


## Predicting GROSS_PROFIT_DEAD_NET

Multi Regression for GROSS_PROFIT_DEAD_NET
```{r}
# Define matrix of predictor variables from train
train_x_P <- data.matrix(train_P[,c("SALES_OFFICE_DESCRIPTION","COUNTY","CUSTOMER_TRADE_CHANNEL_DESCRIPTION","CUSTOMER_SUB_TRADE_CHANNEL_DESCRIPTION","DISCOUNT","MED_HOUSING_COST","MED_INCOME","MED_YEAR_BUILT","MONTHLY_OWNER_COSTS","TOTAL_POP")])

# Define response variable
train_y_P <- train_P$GROSS_PROFIT_DEAD_NET

# Define matrix of predictor variables from test
test_x_P <- data.matrix(test_P[,c("SALES_OFFICE_DESCRIPTION","COUNTY","CUSTOMER_TRADE_CHANNEL_DESCRIPTION","CUSTOMER_SUB_TRADE_CHANNEL_DESCRIPTION","DISCOUNT","MED_HOUSING_COST","MED_INCOME","MED_YEAR_BUILT","MONTHLY_OWNER_COSTS","TOTAL_POP")])
test_y_P <- test_P$GROSS_PROFIT_DEAD_NET

# Multi regression
model_lm_P <- lm(GROSS_PROFIT_DEAD_NET~SALES_OFFICE_DESCRIPTION+COUNTY+CUSTOMER_TRADE_CHANNEL_DESCRIPTION+
                   CUSTOMER_SUB_TRADE_CHANNEL_DESCRIPTION+DISCOUNT++AVG_HOUSEHOLD_SIZE+ MED_INCOME+MED_YEAR_BUILT+MONTHLY_OWNER_COSTS+TOTAL_POP, 
               data = train_P)

#Prediction
lm_P_predictions <- model_lm_P %>% predict(test_P)

# Overall fit of the prediction model,RMSE & R^2 & MAE
lm_fit_P <- postResample(lm_P_predictions, test_P$GROSS_PROFIT_DEAD_NET)

# Overall fit of the prediction model,MSE
mse_lm_P <- mean((test_y_P - lm_P_predictions)^2)
print(paste("Test set mean squared error:", mse_lm_P))
```


Lasso for LONGEVITY
```{r}
#perform k-fold cross-validation to find optimal lambda value
cv_lasso_model_P <- cv.glmnet(train_x_P, train_y_P, alpha = 1, standardize = TRUE, nfolds = 5)

# Find optimal lambda value that minimizes test MSE
best_lambda_lasso_P <- cv_lasso_model_P$lambda.min
best_lambda_lasso_P #399.5965

# Produce plot of test MSE by lambda value
plot(cv_lasso_model_P)

# Find coefficients of best model
best_lasso_model_P <- glmnet(train_x_P, train_y_P, alpha = 1, lambda = best_lambda_lasso_P)
coef(best_lasso_model_P)



# Prediction with lasso
lasso_predictions_test_P <- predict(best_lasso_model_P,s = best_lambda_lasso_P,newx = test_x_P)


# Overall fit of the prediction model,RMSE & R^2 & MAE
lasso_fit_P <-postResample(lasso_predictions_test_P, test_P$GROSS_PROFIT_DEAD_NET)

# Overall fit of the prediction model,MSE
mse_lasso_P <- mean((test_y_P - lasso_predictions_test_P)^2)
print(paste("Test set mean squared error:", mse_lasso_P))
```

Ridge for  GROSS_PROFIT_DEAD_NET
```{r}
# Perform k-fold cross-validation to find optimal lambda value
cv_ridge_P <- cv.glmnet(train_x_P, train_y_P, alpha = 0, standardize = TRUE, nfolds = 5)

# Find optimal lambda value that minimizes test MSE
best_lambda_ridge_P <- cv_ridge_P$lambda.min
best_lambda_ridge_P # 5533.958

# Produce plot of test MSE by lambda value
plot(cv_ridge_P) 

# Find coefficients of best model
best_ridge_model_P <- glmnet(train_x_P, train_y_P, alpha = 0, lambda = best_lambda_ridge_P, standardize = TRUE)
coef(best_ridge_model_P)

# Prediction with ridge
ridge_predictions_test_P <- predict(best_ridge_model_P,s = best_lambda_ridge_P,newx = test_x_P)

# Overall fit of the prediction model,RMSE & R^2 & MAE
ridge_fit_P <- postResample(ridge_predictions_test_P, test_P$GROSS_PROFIT_DEAD_NET)

# Overall fit of the prediction model,MSE
mse_ridge_P <- mean((test_y_P - ridge_predictions_test_P)^2)
print(paste("Test set mean squared error:", mse_ridge_P))

```

ksvm Model for  GROSS_PROFIT_DEAD_NET
```{r}
# Train ksvm model with default settings
set.seed(123)
ksvm_P <- ksvm(train_P$GROSS_PROFIT_DEAD_NET ~ SALES_OFFICE_DESCRIPTION+COUNTY+CUSTOMER_TRADE_CHANNEL_DESCRIPTION+
                   CUSTOMER_SUB_TRADE_CHANNEL_DESCRIPTION+DISCOUNT++AVG_HOUSEHOLD_SIZE+ MED_INCOME+MED_YEAR_BUILT+MONTHLY_OWNER_COSTS+TOTAL_POP,
                data = train_P)

# Overall fit of the prediction model,RMSE & R^2 & MAE
ksvm_predictions_test_P <- predict(ksvm_P,test_P)
ksvm_fit_P <- postResample(ksvm_predictions_test_P, test_P$GROSS_PROFIT_DEAD_NET)

# Overall fit of the prediction model,MSE
mse_ksvm_P <- mean((test_y_P - ksvm_predictions_test_P)^2)
print(paste("Test set mean squared error:", mse_ksvm_P))

```

Gbm Model for GROSS_PROFIT_DEAD_NET
```{r}
# Fit a gradient boosting regression model with 100 trees and 0.01 shrinkage
gbm_P = gbm(train_P$GROSS_PROFIT_DEAD_NET ~SALES_OFFICE_DESCRIPTION+COUNTY+CUSTOMER_TRADE_CHANNEL_DESCRIPTION+
                   CUSTOMER_SUB_TRADE_CHANNEL_DESCRIPTION+DISCOUNT++AVG_HOUSEHOLD_SIZE+ MED_INCOME+MED_YEAR_BUILT+MONTHLY_OWNER_COSTS+TOTAL_POP,
                data = train_P,
                distribution = "gaussian",
                cv.folds = 10,
                shrinkage = .01,
                n.minobsinnode = 10,
                n.trees = 500)
 

gbm_predictions_test_P <- predict.gbm(gbm_P, test_P)

# Evaluate the performance of the model on the test set
gbm_fit_P <- postResample(gbm_predictions_test_P, test_P$GROSS_PROFIT_DEAD_NET)
mse_gbm_P <- mean((test_P$GROSS_PROFIT_DEAD_NET - gbm_predictions_test_P)^2)
print(paste("Random Forest Regression MSE:", mse_gbm_P))
```


## Model results comparison 
Compare the performance for LONGEVITY models
```{r}
# Compare Model fits
lm_fit_L
ksvm_fit_L
gbm_fit_L

# Compare Model MSE
mse_lm_L
mse_ksvm_L
mse_gbm_L
```

Compare the performance for GROSS_PROFIT_DEAD_NET models
```{r}
# Compare Model fits
lm_fit_P
lasso_fit_P
ridge_fit_P
ksvm_fit_P
gbm_fit_P

# Compare Model MSE
mse_lm_P
mse_lasso_P
mse_ridge_P
mse_ksvm_P
mse_gbm_P
```

# Conclusion
Overall, we were able to help the sponsor to develop prediction models for our target variables ( Longevity & Gross_Profit_Dead_Net). We have achieved a great R^2 of 0.84 for Gross_Profit_Dead_Net with GBM model, and For Longevity, our R^2 is not as ideal(KSVM model), however we believe we can optimize it if we are provided with more historical data or census data. Moreover, by examine our prediction models and result we have found that Mexican restaurants, bars and Hamburger restaurants help the company to generate the highest profits. We suggest the company to offer better promotion or discount  when working with potential customers in those three categories, which will help the company to generate more profit in the long-run. We have also discovered that the counties (Box Elder & Summit ) that have the highest customer longevity are both working with Ogden sales, which we suggest the company to investigate what strategy the Ogden office is implementing to acheive a high customer longevity. 